\chapter*{Acknowledgments}

I extend my deepest thanks to my advisors Dr. C. Nataraj and Dr. Xun Jiao for their support and guidance throughout this project, for their encouragement during my pursuit of the ideas contained herein as well as many other ideas, and for their willingness to share their wisdom and experience.  I am further grateful to the additional members of my thesis committee Sean O'Rourke, Principal Member of the Engineering Staff at Lockheed Martin and Dr. Kyle Juretus of the Villanova University Department of Electrical and Computer Engineering (ECE), and to the entire thesis defense audience including my colleagues at the Villanova Center for Analytics of Dynamic Systems (VCADS) and the Villanova ECE department for the stimulating discussions that transpired in response to the first public unveiling of the ideas contained herein, which will in turn surely inspire a number of additional fascinating studies arising from this work.

I am commensurately grateful to all my engineering mentors, colleagues, and friends Rob, Rich, Dave, Jim, Mark, Lydia, Jeff, Gregg, Cindy, Lisa, Lee, Adrian, Henry, John, and Dr. Singh, for their pedagogy, camaraderie, and support which has and will continue to influence the trajectory of my engineering, mathematical, professional, and philosophical development; and am especially grateful to my good friend and mentor Mike Tobits for the countless hours of lessons, co-instructed with Sean, on the pragmatic aspects of engineering over beers at ``Conference Room O" and ``Conference Room J".  To all my professional teammates, Nathan, Jim, Brandon, Mike L., Mike S., Sean B., Steve, John S., and Mirjeta, thank you for sharing an inspiring dedication to the study of signals and systems and the application of artificial intelligence thereto which makes the challenges of simultaneously pursuing both the practical and theoretical aspects of this exciting domain exceptionally rewarding.

I extend a heartfelt thanks to my parents Annette and Mauro, my sister Nicole, my Mommom and my entire family for their encouragement of my ideas and interests from early childhood and throughout my life.  To my grandparents who have passed, my Poppop, my Grandmom Ri, and my Grandpop Morris, I am forever grateful for the life lessons learned and memories passed down, both directly and through the generations.  I owe the foundation from which my thoughts were built, my passion for scientific inquiry and for creative engineering problem solving to the way that I was raised and the way that those who raised me were raised.  I extend equally deep thanks to my friend and brother in kin and in engineering, Steven, and to all my lifelong friends, both in childhood and adulthood, for the past few decades of inspirational memories and bar-closing conversations through which ideas are born and grown.  To my dogs Lola and Coco, I owe you both my thanks along with all the treats in the house and a Fall season filled with weekends running on the beach for keeping me company while writing, no matter how late the hour.

Finally, I wish to dedicate this thesis to my wife Amy for her infinite love and support throughout the writing and development of the body of material contained herein, for her tolerance of the hours spent immersed in depths of higher transcendental functions, and for her unfailing support in all my creative endeavors.  My heart is yours, mi amor, now and forever.

To my family, friends, teachers, and whoever else might read, get forwarded in an email chain, find left on a printer, or otherwise obtain a copy of this thesis and care to skim the acknowledgment section, please accept this as an invitation to share a drink soon. I'll look forward to talks about old memories and new ideas.